
Continue after actually running the main script. This is ment to be an extension to that. 

```{r OTU Significance - Female}
## Kruskal - Wallis test to check for generally significant OTUs ##
OTU_Female <- bCT_Metadata %>%
  select(Sample, Gender) %>% 
  inner_join(OTU_long, by = "Sample") %>% 
  filter(Gender == "F")

## Normal WIlcoxon, paired. Save the significant OTU for each group pair ##
OTU_tests_F <- OTU_Female %>% 
  filter(Group == "PB01" | Group == "PB12") %>% 
  mutate(Sample = substr(Sample, 2, 3)) %>% 
  group_by(OTU) %>% 
  nest() %>% 
  mutate(Wilcox = map(.x = data, ~ wilcox.test(
      x = .x$Abundance[.x$Group == "PB01"],
      y = .x$Abundance[.x$Group == "PB12"],
      paired = TRUE, exact = TRUE) %>%
      tidy())) %>%
  unnest() ## %>%
  # select(Family, Group, p.value) 
  
OTU_tests_F <- OTU_Female %>%
  filter(Group == "LC01" | Group == "LC12") %>% 
  group_by(OTU) %>% 
  nest() %>% 
  mutate(Wilcox = map(.x = data, ~ wilcox.test(
      x = .x$Abundance[.x$Group == "LC01"],
      y = .x$Abundance[.x$Group == "LC12"],
      paired = TRUE, exact = TRUE) %>%
      tidy())) %>%
  unnest() %>%
  # select(Family, Group, p.value) %>%
  bind_rows(., OTU_tests_F)

## Visualise the p values ##
Families_p_values_F <- OTU_tests_F %>%
  ungroup() %>% 
  mutate(Group = substr(Group, 1, 2)) %>% 
  distinct() %>% 
  ggplot(., aes(y = reorder(Family, Abundance), x = p.value, fill = Group)) +
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = c("PB" = Pallete[5], "LC" = Pallete[2])) +
  geom_vline(aes(xintercept = 0.05),
             color = "black",
             linetype = "dotted") +
  scale_x_continuous() +
  labs(y = "Family", x = "P value", title = "Paired Wilcoxon ~ P-Values ~ Females") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_markdown(size = 7, hjust = 1))
```




```{r OTU Significance - Male}
## Kruskal - Wallis test to check for generally significant OTUs ##
OTU_Male <- bCT_Metadata %>%
  select(Sample, Gender) %>% 
  inner_join(OTU_long, by = "Sample") %>% 
  filter(Gender == "M")

## Normal WIlcoxon, paired. Save the significant OTU for each group pair ##
OTU_tests_M <- OTU_Male %>% 
  filter(Group == "PB01" | Group == "PB12") %>% 
  mutate(Sample = substr(Sample, 2, 3)) %>% 
  group_by(OTU) %>% 
  nest() %>% 
  mutate(Wilcox = map(.x = data, ~ wilcox.test(
      x = .x$Abundance[.x$Group == "PB01"],
      y = .x$Abundance[.x$Group == "PB12"],
      paired = TRUE, exact = TRUE) %>%
      tidy())) %>%
  unnest() ## %>%
  # select(Family, Group, p.value) 
  
OTU_tests_M <- OTU_Male %>%
  filter(Group == "LC01" | Group == "LC12") %>% 
  group_by(OTU) %>% 
  nest() %>% 
  mutate(Wilcox = map(.x = data, ~ wilcox.test(
      x = .x$Abundance[.x$Group == "LC01"],
      y = .x$Abundance[.x$Group == "LC12"],
      paired = TRUE, exact = TRUE) %>%
      tidy())) %>%
  unnest() %>%
  # select(Family, Group, p.value) %>%
  bind_rows(., OTU_tests_M)

## Visualise the p values ##
Families_p_values_M <- OTU_tests_M %>%
  ungroup() %>% 
  mutate(Group = substr(Group, 1, 2)) %>% 
  distinct() %>% 
  ggplot(., aes(y = reorder(Family, Abundance), x = p.value, fill = Group)) +
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = c("PB" = Pallete[5], "LC" = Pallete[2])) +
  geom_vline(aes(xintercept = 0.05),
             color = "black",
             linetype = "dotted") +
  scale_x_continuous() +
  labs(y = "Family", x = "P value", title = "Paired Wilcoxon ~ P-Values ~ Males") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_markdown(size = 7, hjust = 1))
```


```{r Gendered Alpha Significance }
## Perform the t tests ##
## In case you want to also make tests for each gender, add two lines in the filter ##
## section of each command and alter the preexisting ones to cover the genders. ##
Metadata_Indexes_F <- bCT_Metadata %>%
  select(Sample, Gender) %>% 
  inner_join(Metadata_Indexes, by = "Sample") %>% 
  filter(Gender == "F") %>% 
  select(-Gender)

Pairwise_Index_t_F <- Metadata_Indexes_F %>%
  nest() %>%
  mutate(t_test = map(.x = data, ~ pairwise.t.test(
      x = .x$Shannon, g = .x$Group, p.adjust.method = "none") %>% 
        tidy())) %>% 
  unnest(t_test) %>% 
  filter((group1 == "LC12" & group2 == "LC01") |
         (group1 == "PB12" & group2 == "PB01")) %>% 
  mutate(Shannon_p = p.value) %>% 
  select(-p.value, -data)

Pairwise_Index_t_F$Simpson_p <- Metadata_Indexes_F %>%
  nest() %>%
  mutate(t_test = map(.x = data, ~ pairwise.t.test(
    x = .x$Simpson, g = .x$Group, p.adjust.method = "none") %>% 
      tidy())) %>% 
  unnest(t_test) %>% 
  filter((group1 == "LC12" & group2 == "LC01") |
         (group1 == "PB12" & group2 == "PB01")) %>% 
  mutate(Simpson_p = p.value) %>% 
  pull(Simpson_p)

Pairwise_Index_t_F$Inv_Simpson_p <- Metadata_Indexes_F %>%
  nest() %>%
  mutate(t_test = map(.x = data, ~ pairwise.t.test(
    x = .x$Inverse_Simpson, g = .x$Group, p.adjust.method = "none") %>% 
      tidy())) %>% 
  unnest(t_test) %>% 
  filter((group1 == "LC12" & group2 == "LC01") |
         (group1 == "PB12" & group2 == "PB01")) %>% 
  mutate(Inv_Simpson_p = p.value) %>% 
  pull(Inv_Simpson_p)

Pairwise_Index_t_F$Pielou_p <- Metadata_Indexes_F %>%
  nest() %>%
  mutate(t_test = map(.x = data, ~ pairwise.t.test(
    x = .x$Pielou, g = .x$Group, p.adjust.method = "none") %>% 
      tidy())) %>% 
  unnest(t_test) %>% 
  filter((group1 == "LC12" & group2 == "LC01") |
         (group1 == "PB12" & group2 == "PB01")) %>% 
  mutate(Pielou_p = p.value) %>% 
  pull(Pielou_p)
```

```{r Gendered Alpha Significance }
## Perform the t tests ##
## In case you want to also make tests for each gender, add two lines in the filter ##
## section of each command and alter the preexisting ones to cover the genders. ##
Metadata_Indexes_M <- bCT_Metadata %>%
  select(Sample, Gender) %>% 
  inner_join(Metadata_Indexes, by = "Sample") %>% 
  filter(Gender == "M") %>% 
  select(-Gender)

Pairwise_Index_t_M <- Metadata_Indexes_M %>%
  nest() %>%
  mutate(t_test = map(.x = data, ~ pairwise.t.test(
      x = .x$Shannon, g = .x$Group, p.adjust.method = "none") %>% 
        tidy())) %>% 
  unnest(t_test) %>% 
  filter((group1 == "LC12" & group2 == "LC01") |
         (group1 == "PB12" & group2 == "PB01")) %>% 
  mutate(Shannon_p = p.value) %>% 
  select(-p.value, -data)

Pairwise_Index_t_M$Simpson_p <- Metadata_Indexes_M %>%
  nest() %>%
  mutate(t_test = map(.x = data, ~ pairwise.t.test(
    x = .x$Simpson, g = .x$Group, p.adjust.method = "none") %>% 
      tidy())) %>% 
  unnest(t_test) %>% 
  filter((group1 == "LC12" & group2 == "LC01") |
         (group1 == "PB12" & group2 == "PB01")) %>% 
  mutate(Simpson_p = p.value) %>% 
  pull(Simpson_p)

Pairwise_Index_t_M$Inv_Simpson_p <- Metadata_Indexes_M %>%
  nest() %>%
  mutate(t_test = map(.x = data, ~ pairwise.t.test(
    x = .x$Inverse_Simpson, g = .x$Group, p.adjust.method = "none") %>% 
      tidy())) %>% 
  unnest(t_test) %>% 
  filter((group1 == "LC12" & group2 == "LC01") |
         (group1 == "PB12" & group2 == "PB01")) %>% 
  mutate(Inv_Simpson_p = p.value) %>% 
  pull(Inv_Simpson_p)

Pairwise_Index_t_M$Pielou_p <- Metadata_Indexes_M %>%
  nest() %>%
  mutate(t_test = map(.x = data, ~ pairwise.t.test(
    x = .x$Pielou, g = .x$Group, p.adjust.method = "none") %>% 
      tidy())) %>% 
  unnest(t_test) %>% 
  filter((group1 == "LC12" & group2 == "LC01") |
         (group1 == "PB12" & group2 == "PB01")) %>% 
  mutate(Pielou_p = p.value) %>% 
  pull(Pielou_p)
```




Paired Wilcox tests for all groups. Check for significant differences between OTUs with the Kruskal Wallis test first and then pipe the ones with a P-value < 0.05 to the Wilcoxon test. In case you have multiple comparisons between multiple groups, change the test to a pairwise Wilcoxon using the supplementary code. Keep in mind that this will require a p-adjustment. 

```{r OTU Significance ~ Phylum}
## Kruskal - Wallis test to check for generally significant OTUs ##
OTU_Phylum_long_F <- bCT_Metadata %>%
  select(Sample, Gender) %>% 
  inner_join(OTU_Phylum_long, by = "Sample") %>% 
  filter(Gender == "F") %>% 
  select(-Gender)

OTU_Phylum_long_M <- bCT_Metadata %>%
  select(Sample, Gender) %>% 
  inner_join(OTU_Phylum_long, by = "Sample") %>% 
  filter(Gender == "M") %>% 
  select(-Gender)

## Normal WIlcoxon, paired. Save the significant OTU for each group pair ~ Female ##
Phyla_tests_F <- OTU_Phylum_long_F %>% 
  filter(Group == "PB01" | Group == "PB12") %>% 
  mutate(Sample = substr(Sample, 2, 3)) %>% 
  group_by(Phylum) %>% 
  nest() %>% 
  mutate(Wilcox = map(.x = data, ~ wilcox.test(
      x = .x$Abundance[.x$Group == "PB01"],
      y = .x$Abundance[.x$Group == "PB12"],
      paired = TRUE, exact = TRUE) %>%
      tidy())) %>%
  unnest()
  
Phyla_tests_F <- OTU_Phylum_long_F %>%
  filter(Group == "LC01" | Group == "LC12") %>% 
  group_by(Phylum) %>% 
  nest() %>% 
  mutate(Wilcox = map(.x = data, ~ wilcox.test(
      x = .x$Abundance[.x$Group == "LC01"],
      y = .x$Abundance[.x$Group == "LC12"],
      paired = TRUE, exact = TRUE) %>%
      tidy())) %>%
  unnest() %>%
  # select(Family, Group, p.value) %>%
  bind_rows(., Phyla_tests_F)

## Normal WIlcoxon, paired. Save the significant OTU for each group pair ~ Male ##
Phyla_tests_M <- OTU_Phylum_long_M %>% 
  filter(Group == "PB01" | Group == "PB12") %>% 
  mutate(Sample = substr(Sample, 2, 3)) %>% 
  group_by(Phylum) %>% 
  nest() %>% 
  mutate(Wilcox = map(.x = data, ~ wilcox.test(
      x = .x$Abundance[.x$Group == "PB01"],
      y = .x$Abundance[.x$Group == "PB12"],
      paired = TRUE, exact = TRUE) %>%
      tidy())) %>%
  unnest()
  
Phyla_tests_M <- OTU_Phylum_long_M %>%
  filter(Group == "LC01" | Group == "LC12") %>% 
  group_by(Phylum) %>% 
  nest() %>% 
  mutate(Wilcox = map(.x = data, ~ wilcox.test(
      x = .x$Abundance[.x$Group == "LC01"],
      y = .x$Abundance[.x$Group == "LC12"],
      paired = TRUE, exact = TRUE) %>%
      tidy())) %>%
  unnest() %>%
  # select(Family, Group, p.value) %>%
  bind_rows(., Phyla_tests_M)

## Visualise the p values ##
Phyla_p_values_F <- Phyla_tests_F %>%
  ungroup() %>%
  mutate(Group = substr(.$Group, 1, 2)) %>%
  ggplot(., aes(y = reorder(Phylum, Abundance), x = p.value, fill = Group)) +
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = c("PB" = Pallete[5], "LC" = Pallete[2])) +
  geom_vline(aes(xintercept = 0.05),
             color = "black",
             linetype = "dotted") +
  scale_x_continuous() +
  labs(y = "Phylum", x = "P value", title = "Paired Wilcoxon ~ P-Values ~ Females") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_markdown(size = 7, hjust = 1))

Phyla_p_values_M <- Phyla_tests_M %>%
  ungroup() %>%
  mutate(Group = substr(.$Group, 1, 2)) %>%
  ggplot(., aes(y = reorder(Phylum, Abundance), x = p.value, fill = Group)) +
  geom_point(shape = 21, size = 2) +
  scale_fill_manual(values = c("PB" = Pallete[5], "LC" = Pallete[2])) +
  geom_vline(aes(xintercept = 0.05),
             color = "black",
             linetype = "dotted") +
  scale_x_continuous() +
  labs(y = "Phylum", x = "P value", title = "Paired Wilcoxon ~ P-Values ~ Males") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_markdown(size = 7, hjust = 1))

```

```{r}
## Alpha Significance ##
Pairwise_Index_t_F
Pairwise_Index_t_M
## Families - Significance ##
Families_p_values_F
Families_p_values_M
## Phyla - Significance ##
Phyla_p_values_F
Phyla_p_values_M

# ggsave("Plottin_2/Gendered/Families_p_values_F.png", plot = Families_p_values_F, width = 12, height = 8, dpi = 600)
# ggsave("Plottin_2/Gendered/Families_p_values_M.png", plot = Families_p_values_M, width = 12, height = 8, dpi = 600)
# ggsave("Plottin_2/Gendered/Phyla_p_values_F.png", plot = Phyla_p_values_F, width = 12, height = 8, dpi = 600)
# ggsave("Plottin_2/Gendered/Phyla_p_values_M.png", plot = Phyla_p_values_M, width = 12, height = 8, dpi = 600)
```



```{r Alpha diversity plots}
## Indexes - Barplots
Alpha_Div_Barplots_Gendered <- Metadata_Indexes %>%
  mutate(Gender = bCT_Metadata$Gender) %>%
  pivot_longer(cols = -c(Sample, Group, Gender), names_to = "Index", values_to = "Value") %>% 
  inner_join(Index_Stats, by = c("Group", "Index")) %>% 
  filter(!Gender == "U") %>%
  ggplot(., aes(x = Group, y = Value, fill = Group)) + 
  geom_col(data = Index_Stats, aes(x = Group, y = Median, fill = Group), 
           position = position_dodge(width = 0.75), width = 0.6, alpha = 0.8) +
  scale_fill_manual(values = color_palette_function(length(unique(Metadata_Indexes$Group)))) +  
  # geom_boxplot(alpha = 0.8) + 
  geom_jitter(width = 0, alpha = 0.3, colour = "midnightblue") +
  ggh4x::facet_grid2(Gender ~ Index, scales = "free", independent = "y") + 
  theme(plot.title = element_text(hjust = 0.5),
        panel.background = element_rect(fill = "grey75"),
        axis.title.x = element_blank(), axis.text.x = element_text(size = 8, angle = 45, hjust = 1)) + 
  ggtitle("Alpha Diversity Indexes ~ Divided by Gender") + 
  guides(fill = guide_legend(ncol = 1)) +
  labs(fill = "Group") + 
  stat_compare_means(method = "t.test", paired = TRUE, label = "p.signif",
                     comparisons = list( c("PB01", "PB12"), c("LC01", "LC12"))) +
  geom_errorbar(aes(ymin = Min, ymax = Max), width = 0.2)


## Indexes - Boxplots
Alpha_Div_Boxplots_Gendered <- Metadata_Indexes %>%
  mutate(Gender = bCT_Metadata$Gender) %>% 
  pivot_longer(cols = -c(Sample, Group, Gender), names_to = "Index", values_to = "Value") %>% 
  filter(!Gender == "U") %>%
  ggplot(., aes(x = Group, y = Value, fill = Group)) + 
    geom_boxplot(alpha = 0.8) + geom_jitter(width = 0, alpha = 0.6, colour = "mediumblue") +
    scale_fill_manual(values = color_palette_function(length(unique(Metadata_Indexes$Group)))) +  
    ggh4x::facet_grid2(Gender ~ Index, scales = "free", independent = "y") + 
    theme(plot.title = element_text(hjust = 0.5),
          panel.background = element_rect(fill = "grey75"),
          axis.title.x = element_blank(), axis.text.x = element_text(size = 8, angle = 45, hjust = 1)) + 
    ggtitle("Alpha Diversity Indexes") + 
    guides(fill = guide_legend(ncol = 1)) +
    labs(fill = "Group") + 
  stat_compare_means(method = "t.test", paired = TRUE, label = "p.signif",
                     comparisons = list( c("PB01", "PB12"), c("LC01", "LC12")))

# ggsave("Plottin_2/Gendered/Alpha_Div_Barplots_Gendered.png", plot = Alpha_Div_Barplots_Gendered, width = 12, height = 8, dpi = 600)
# ggsave("Plottin_2/Gendered/Alpha_Div_Boxplots_Gendered.png", plot = Alpha_Div_Boxplots_Gendered, width = 12, height = 8, dpi = 600)

```

